Stack Safety as a Security Property

### 2020-07-07 main.tex
Found some mismatched color names
Eager vs lazy policies

For an example see \cref{fig:intex}, representing the unsafe substitution
\[
  44: ~ \sw ~ \rsp ~ r_4 ~ -5
\]
This instruction is in {\tt h}, and instead of storing data to the return,
it overwrites {\tt g}'s variable, {\tt z}. At the top of the figure high
integrity memory is in red, while low integrity is in green; at the end of the
trace address 103 should match the initial state, and does not. So trace
integrity is violated.

@@

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in red and low confidentiality in green. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but the rest might have
any value, in yellow. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in pink, and while 109
is consistent, 108 will not hold 43 in all variants, so the trace does not obey
trace confidentiality.

@@

@@

\rb{This part should probably be somewhere in the lazy section.}
%
In practice, this \emph{eager policy} is too slow to be of practical interest:
what we really want in practice is a \emph{lazy policy} that can be efficiently
implemented.

Less conservative policies can be more efficient, but also harder to test.

We can also test the lazy policy, even if less efficiently, and it should
enforce an inductive property, which may be more amenable to proving.
%
\rb{Would need careful phrasing.}
%
\rb{Implied by the property we started with?}

@@

\rb{The Static Authorities differs from the Depth Isolation policy in that frame
  ids aren't true activation ids, but unique ids associated to all activations
  of the same function. Discuss unique activation ids and compare with depth
  later, possibly when discussing lazy policies, as the difference becomes
  tangible there.}

@@

    For out example, we return to the violation of trace integrity in
    \cref{fig:intex}, in which {\tt h} has written to {\tt z} and returned.
    Whether observable integrity holds depends on the continuing trace, shown
    in \cref{fig:intlex}. Above, we have the final state of \(\MPT\),
    \(\mach_r\), with high integrity components in red and low integrity in
    green. Next is the rolled-back state, \(\mach_r' =
    \mathit{roll}(\contour,\mach_e,\mach_r)\), in which high integrity
    components are restored to their values as of \(\mach_e\). Specifically,
    address 103 is restored to 0. When instruction 31 prints {\tt z} in the
    trace from \(\mach_r\), it prints 18, but in the trace from \(\mach_r'\)
    it prints 0. So observable trace integrity does not hold.

@@

      In our example, \cref{fig:conflex} shows how execution continues from
      \(\mach_r'\) and the restored \(\mach_r'' = \mathit{restore}(\contour,
      \mach_e,\mach_e',\mach_r,\mach_r')\). Addresses 108 and 109, in pink, are
      not restored; every address that was varied and not changed in one of the
      executions is. Since 108 contains a value that originates in the
      variation, values that depend on it might be anything; after returning
      from {\tt g}, {\tt main} prints 95 in the trace from \(\mach_r\) and
      some undetermined value in the trace from \(\mach_r''\). So observable
      trace confidentiality does not hold.

>>>>

For an example see \cref{fig:intex}, representing the unsafe substitution
\[
  44: ~ \sw ~ \rsp ~ r_4 ~ -5
\]
This instruction is in {\tt h}, and instead of storing data to the return,
it overwrites {\tt g}'s variable, {\tt z}. At the top of the figure high
integrity memory is in red, while low integrity is in green; at the end of the
trace address 103 should match the initial state, and does not. So trace
integrity is violated.
\rb{There are some color name macros, but none for integrity yet? Use instead
of hardcoded color names.}

@@

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in red and low confidentiality in green. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but the rest might have
any value, in yellow. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in pink, and while 109
is consistent, 108 will not hold 43 in all variants, so the trace does not obey
trace confidentiality.
\rb{Color name macros}

@@

Integrity

Confidentiality as a form of noninterference

@@

The conservative policy we just described, while testable and enforceable, is
too slow to be of practical use. What we want, instead, is a somewhat more
permissive policy that moreover can be efficiently implemented. Most of the
performance overhead incurred by this kind of \emph{eager policy} steps from the
need to set stack activation tags as a frame is created and reset them as it is
destructed, as \citet{DBLP:conf/sp/RoesslerD18} confirm in their evaluation. To
mitigate those costs, they propose optimizations like Lazy Tagging and Lazy
Clearing that relax and defer some of the checks of an eager policy, being more
permissive in their allowed operations and catching violations if and when their
effect becomes manifest.
\rb{How much detail to go into? Refer to examples if we have the space?}

These \emph{lazy policies} admit more efficient implementations while being
harder to test, given that potential violations may or may not materialize,
requiring in turn additional bookkeeping. However, a critical observation is
that the depth-based tagging scheme discussed so far with fail when combined
with a lazy policy. The reason for this is that because tags are not set and
cleared on function entry and exit points, stale tags may persist after a given
call, and a subsequent call sharing the same depth as the old call may access
memory contents tagged with the stale tags of a previous activation.
\rb{Again, example?}

The lazy policy can be repaired if, instead of tagging each function activation
with its depth in the stack, we generate a fresh activation identifier on each
call, which allows the policy to identify stale tags from previous activations.
Under this stricted tagging discipline, the eager policy behaves almost exactly
like its lazy counterpart. A related mechanism was explored in the Static
Authorities policy of \citet{DBLP:conf/sp/RoesslerD18}, which associates a
unique activation identifier to each function, which is however shared by all
activations of the same function in order to obtain good cacheability of tag
rules.

\rb{Parts of this discussion feel somewhat out of order...}

\rb{We can also test the lazy policy, even if less efficiently, and it should
  enforce an inductive property, which may be more amenable to proving --- this
  should be the connection to the following section.}

\rb{Implied by the property we started with?}

@@

@@

    For out example, we return to the violation of trace integrity in
    \cref{fig:intex}, in which {\tt h} has written to {\tt z} and returned.
    Whether observable integrity holds depends on the continuing trace, shown
    in \cref{fig:intlex}. Above, we have the final state of \(\MPT\),
    \(\mach_r\), with high integrity components in red and low integrity in
    green. Next is the rolled-back state, \(\mach_r' =
    \mathit{roll}(\contour,\mach_e,\mach_r)\), in which high integrity
    components are restored to their values as of \(\mach_e\). Specifically,
    address 103 is restored to 0. When instruction 31 prints {\tt z} in the
    trace from \(\mach_r\), it prints 18, but in the trace from \(\mach_r'\)
    it prints 0. So observable trace integrity does not hold.
    \rb{Color name macros}

@@

      In our example, \cref{fig:conflex} shows how execution continues from
      \(\mach_r'\) and the restored \(\mach_r'' = \mathit{restore}(\contour,
      \mach_e,\mach_e',\mach_r,\mach_r')\). Addresses 108 and 109, in pink, are
      not restored; every address that was varied and not changed in one of the
      executions is. Since 108 contains a value that originates in the
      variation, values that depend on it might be anything; after returning
      from {\tt g}, {\tt main} prints 95 in the trace from \(\mach_r\) and
      some undetermined value in the trace from \(\mach_r''\). So observable
      trace confidentiality does not hold.
      \rb{Color name macro}
